Algebraic Filtering of Surfaces from 3D Medical Images with Julia

### 2020-04-26 src/examples.tex
Updates from Overleaf

% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\begin{figure}
\centering
% \includegraphics[width=0.3\textwidth]{figs/ircad01}
\includegraphics[width=0.4\textwidth]{figs/liver_01_red_3.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/portalvein_01_yellow_3.png} 
% \vspace{0.01\textwidth}
\includegraphics[height=0.4\textwidth]{src/figs/nrn10_100_magenta_high_res.png} 
% \includegraphics[height=0.4\textwidth]{figs/nrn10_100_low_res.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
\caption{
Triangulated isosurface of liver parts extracted with LAR-SURF algorithm. 
On the upper left image the surface of the liver parenchyma of human can be seen. 
Both right images show the Portal Vein from the same Ircad dataset \cite{ircad} 
with resolution $1.6\times0.57\times0.57$ [mm].
On the left bottom image is the pig liver microvasculature based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The resolution of the Micro-CT data is 4.682 $\mu{}m$.
} \label{fig:example_liver_macro_micro}
\end{figure}

>>>>

% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{src/figs/ircad01_segmentation_65.png}
\includegraphics[width=0.45\textwidth]{src/figs/ircad01_liver_tricolore_01.png}
\includegraphics[width=0.45\textwidth]{src/figs/ircad01_porta_blue_01.png}
\includegraphics[width=0.45\textwidth]{src/figs/nrn10_200_pink_02.png}
% \includegraphics[width=0.4\textwidth]{figs/liver_01_red_3.png} 
% % \vspace{0.05\textwidth}
% \includegraphics[width=0.4\textwidth]{figs/portalvein_01_yellow_3.png} 
% % \vspace{0.01\textwidth}
% \includegraphics[height=0.4\textwidth]{src/figs/nrn10_100_magenta_high_res.png} 
% % \includegraphics[height=0.4\textwidth]{figs/nrn10_100_low_res.png} 
% % \vspace{0.05\textwidth}
% \includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
\caption{
Liver structures. The upper left image shows one slice  with segmented organs from  the Ircad dataset \cite{ircad}.
The other images show the triangulated isosurfaces of the macroscopic and microscopic strucures of the liver extracted with \textsc{lar-surf} algorithm. 
On the upper right image can be seen the wire frame model of the human liver along with portal vein and hepatic artery. 
% Both right images show the Portal Vein from the same Ircad dataset \cite{ircad} 
The left bottom image shows the detail of the portal vein  
with resolution $1.6\times0.57\times0.57$ $[mm]$.
On the bottom right image is shown the microvasculature of a pig liver based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The size of the speciment is 0.936 $[mm]$ along each axis and the resolution of the Micro-CT data is 4.682 $\mu{}m$.
} \label{fig:example_liver_macro_micro}
\end{figure}
